Checkpoint 4

### 2020-04-29 Checkpoint 4.Rmd
to do now

@@

\
\

@@

```{r}
# Pct black, Neg Rate: Random effects
model_17<-stan_glmer(
  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
  data = mod_data, family = gaussian, chains = 4, iter = 2*5000
)
```

```{r}
head(data.frame(summary(model_17)),-2)
```

@@

ggplot(model_17_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

>>>>

```{r}
################################## To do before Alicia with your fave model ##########################################
# mcmc_trace()
# mcmc_dens_overlay()
# pp_check()

### For predicting one case 
          # new_308 <- data.frame(Days = 9, Subject =308)
          # 
          # set.seed(454)
          # pred_308 <- posterior_predict(
          #   model_4, 
          #   newdata = new_308)
          # 
          # pred_308 <- data.frame(y_new = pred_308[-1])
          # 
          # ggplot(pred_308, aes(x=y_new))+geom_density()
          # 
          # summary(pred_308)

## For correlation check (type like model 2 from activity 19)
          # Store the chains
          # model_1_df <- as.array(model_1) %>% 
          #   melt %>% 
          #   pivot_wider(names_from = parameters, values_from = value)
          # 
          # # Wrangle the chains
          # # Note the need for `...` around the sigma_sq_b
          # model_1_df <- model_1_df %>% 
          #   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[Region:(Intercept),(Intercept)]`) %>% 
          #   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
          # 
          # ggplot(model_1_df, aes(x = correlation)) + 
          #   geom_density(alpha = 0.5)
```

```{r, include=FALSE}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}

prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # This function summarizes the predictions across all cases
  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
    mutate(error = y - post_median) %>% 
    mutate(error_scaled = error / post_mad) %>% 
    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
    mutate(within_outer = (y >= l_outer) & (y <= u_outer))

  pred_summary <- pred_data %>% 
    summarize(mae = median(abs(error)), 
      mae_scaled = median(abs(error_scaled)),
      within_inner = mean(within_inner),
      within_outer = mean(within_outer)
    )
  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
  names(pred_summary)[4] <- paste0("within_", prob_outer*100)

  pred_summary
}
```

@@

```{r, warning = FALSE, cache=TRUE}
model_5 <- stan_glmer(
  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)

@@

```{r}
# Pct black, Neg Rate: Random effects
model_17<-stan_glmer(
  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
  data = mod_data, family = gaussian, chains = 4, iter = 2*5000

)
```

```{r}

head(data.frame(summary(model_5),-2))

head(data.frame(summary(model_17)),-2)
```

@@

ggplot(model_17_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
